Verifying Demonstrations

### 2019-02-21 paper/protocol.tex
Changes phrasing in protocol regarding unclonable subscriptions

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key, in other words an uncloneable
subscription to one's identity\footnote{%
  Given any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack}, systems such as \cite{clonewars} could
  be used to make sure that for each identity one-and-only-one
  cryptographic key is issued. 
}. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key, more specifically, an anonymous 
identity credential that provides unlinkability between contexts but 
linkability for reuse within the same context\footnote{%
  Given any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
  be used to make sure that for each identity one-and-only-one
  cryptographic key is issued.
  In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
  to one's identity.
}. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.
